# Article information

Experimental data for "Colorful glares Effects of colors on brightness illusions measured with pupillometry"

Yuta Suzuki, Bruno Laeng, Tetsuto Minami, Shigeki Nakauchi

*Corresponding author: Yuta Suzuki
Department of Computer Science and Engineering, Toyohashi University of Technology, 1-1 Hibarigaoka Tempaku, Toyohashi, Aichi 441-8580, Japan
E-mail address: suzuki14@vpac.cs.tut.ac.jp

# Package instalation
```{r, message=FALSE, warning=FALSE}
library(rjson)
library(ggplot2)
library(ggpubr)
library(Cairo)
library(R.matlab)
library(lme4)
library(lmerTest)

if(exists(".anovakun.env")){
  sys.source("./data/anovakun_485.R", envir = .anovakun.env)
}else{
  .anovakun.env <- new.env()
  sys.source("./data/anovakun_485.R", envir = .anovakun.env)
  attach(.anovakun.env)
}
subName = NULL
for( i in seq(30)){ 
  if(i<10){subName = rbind(subName,paste("s0", i, sep = ""))} 
  else{subName = rbind(subName,paste("s", i, sep = ""))}
}

```

# Function definition
```{r, message=FALSE, warning=FALSE}
combineGraphs <- function(graphNum,p,layout){
  
  titleStr = c("'(a)'", "'(b)'", "'(c)'", "'(d)'", "'(e)'", "'(f)'", "'(g)'")
  st = paste(p,graphNum, sep = "", collapse=",")
  labelSt = titleStr[seq(1,length(graphNum))]
  labelSt = paste(labelSt, collapse=",")
  
  ncolNum = round(length(graphNum) / 2 )
  
  if (is.numeric(layout)){
    eval(parse(text=paste("p = grid.arrange(", 
                          st ,",layout_matrix = layout)",
                          sep="")))
  }else{
    eval(parse(text=paste("p = ggarrange(",
                          st ,",labels = c(",
                          labelSt,
                          "),ncol = 2, nrow =", ncolNum, ")",
                          sep="")))
  }
  return(p)
}

makePupilDataset_mat2long <- function(dat,nameOfVar, timeLen,fNum,orderName,factors){
  
  numOfTrial = dim(dat$y)[1]
  numOfSub = length(unique(dat$sub))
  lengthOfTime = dim(dat$y)[2]
  
  sTime = timeLen[1]
  eTime = timeLen[2]
  
  x = seq(sTime,eTime,length=lengthOfTime)
  
  ind_data <- data.frame(
    sub =  rep( dat$sub, times = rep( lengthOfTime, numOfTrial)),
    data_y = t(matrix(t(dat$y),nrow=1)),
    data_x = x
  )
  
  if (length(nameOfVar)  == 1){
    eval(parse(text=paste("ind_data$",factors[[1]],"=",
                          "rep( fNum[[1]][dat$",nameOfVar[[1]],"], times = rep(lengthOfTime, numOfTrial))",
                          sep="")))
    
    eval(parse(text=paste("ind_data$",factors[[1]],"<-",
                          "factor(ind_data$", factors[[1]],",levels = orderName[[1]])", sep="")))
    
  }else{
    eval(parse(text=paste("ind_data$",factors[[1]],"=",
                          "rep( fNum[[1]][dat$", nameOfVar[[1]],"], times = rep(lengthOfTime, numOfTrial))",
                          sep="")))
    eval(parse(text=paste("ind_data$",factors[[2]],"=",
                          "rep( fNum[[2]][dat$" , nameOfVar[[2]], "], times = rep(lengthOfTime, numOfTrial))",
                          sep="")))
    
    eval(parse(text=paste("ind_data$",factors[[1]],"<-",
                          "factor(ind_data$", factors[[1]],",levels = orderName[[1]])", sep="")))
    eval(parse(text=paste("ind_data$",factors[[2]],"<-",
                          "factor(ind_data$", factors[[2]],",levels = orderName[[2]])", sep="")))
  }
  
  return(ind_data)
}

setFigureStyle <- function(gData,size_font=20){
  gData <- gData +theme(
    axis.title.x = element_text(size=size_font),
    axis.title.y = element_text(size=size_font),
    axis.line = element_line(colour = "black"),
    axis.text.x = element_text(colour="black"),
    axis.text.y = element_text(colour="black"),
    panel.background = element_rect(fill = "transparent",color = 'black',size = 0.5),
    panel.grid.major = element_line(colour = "gray", size = 0.05),
    panel.grid.minor = element_line(colour = NA),
    axis.ticks = element_line(colour = "black",size = 0.5),
    text = element_text(size = size_font,family = "Times"),
    # text = element_text(size = size_font,family = "Source Han Sans JP ExtraLight"),
    # text = element_text(size = 16,family = "Helvetica"),
    legend.title = element_text(size=(size_font/3)),
    legend.text = element_text(size=(size_font/2)),
    legend.key=element_rect(colour="transparent", fill=NA),
    plot.background=element_rect(fill="transparent", colour=NA),
    legend.background=element_rect(fill="transparent", colour=NA),
    plot.title = element_text(size = size_font)
    # axis.line = element_line(colour = 'black', size = 2)
  )
  return(gData)
}

setBarFigureStyle <- function(gData,size_font=20){
  gData <- gData +theme(
    axis.title.x = element_text(size=size_font),
    axis.title.y = element_text(size=size_font),
    panel.border = element_blank(), 
    axis.line = element_line(),
    axis.text.x = element_text(colour="black"),
    axis.text.y = element_text(colour="black"),
    panel.background = element_rect(fill = "transparent",size = 0.5),
    # panel.grid.major = element_line(colour = NA),
    panel.grid.major.y = element_line(colour = "gray", size = 0.05),
    panel.grid.major.x = element_line(colour = NA),
    panel.grid.minor = element_line(colour = NA),
    axis.ticks = element_line(colour = "black",size = 0.5),
    text = element_text(size = size_font,family = "Times"),
    # text = element_text(size = size_font,family = "Source Han Sans JP ExtraLight"),
    legend.title = element_text(size=(size_font/2)),
    legend.text = element_text(size=(size_font/2)),
    legend.key=element_rect(colour="transparent", fill=NA),
    plot.background=element_rect(fill="transparent", colour=NA),
    legend.background=element_rect(fill="transparent", colour=NA),
    plot.title = element_text(size = size_font)
    )
  return(gData)
}

disp <- function(ribbondata,config,shadeFl,factors,numOfSub=0){
  
  if (shadeFl == 1) {
    if(numOfSub == 0) {numOfSub = length(unique(ribbondata$sub))}
    eval(parse(text=paste(
      "data_std = aggregate( data_y ~ data_x * ",factors[1],"*",factors[2],
      ", data = ribbondata, FUN = 'sd')",
      sep=""))) 
    eval(parse(text=paste(
      "ribbondata = aggregate( data_y ~ data_x * ",factors[1],"*",factors[2],
      ", data = ribbondata, FUN = 'mean')",
      sep="")))
    
    data_std$data_y <- data_std$data_y / sqrt(numOfSub)
    ribbondata$ymin <- ribbondata$data_y - data_std$data_y
    ribbondata$ymax <- ribbondata$data_y + data_std$data_y
    
    eval(parse(text=paste(
      "p <- ggplot(ribbondata,
      aes(x = data_x, y = data_y, colour = ", factors[1],", group = ",factors[1],"))+",
      # "annotation_raster(image, -Inf, Inf, -Inf, Inf) +",
      "geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = ",factors[2],", group = ",factors[1], "), color = 'gray', fill = 'gray', alpha = config$alpha, size = 0.05) +",
      "geom_line()",
      # "geom_line(aes(linetype=",factors[1],"))",
      sep="")))
    
    if(!is.null(config$grCol)){
      p <- p +
        # scale_color_manual(values = config$grCol, name = factors[1])+
        scale_fill_manual(values = config$grCol)+
        scale_color_manual(values = config$grCol)
    }
    
    p <- p +
      ggtitle(config$title) +
      xlab(config$label_x) + ylab(config$label_y) +
      coord_cartesian(xlim = config$lim_x,ylim = config$lim_y) +
      scale_x_continuous(expand = c(0, 0)) 
    
  }else{ 
    
    eval(parse(text=paste(
      "p <- ggplot(ribbondata,aes(x = data_x, y = data_y, colour = ", factors[1],", group = ",factors[2],"))+", 
      # "geom_line(aes(linetype = Type))",
      "geom_line()",
      sep="")))
    
    if(!is.null(config$grCol)){
      p <- p +
        scale_color_manual(values = config$grCol)
    }
    p <- p + 
      geom_vline(xintercept=0, colour='black', linetype='longdash', size = 0.1) +
      ggtitle(config$title) +
      xlab(config$label_x) + ylab(config$label_y) +
      coord_cartesian(xlim=config$lim_x, ylim=config$lim_y) +
      scale_x_continuous(expand = c(0, 0))
    # scale_y_continuous(expand = c(0, 0.1))
    # scale_y_continuous(breaks = seq(config$lim_y[1],config$lim_y[2],config$stride),expand = c(0, 0))
    
  }
  
  p = setBarFigureStyle(p)
  
  return(p)
}


dispLineGraph <- function(ribbondata, config, factors,numOfSub = 0){
  
  if(numOfSub == 0) {numOfSub = length(unique(ribbondata$sub))}
  
  if(length(factors) == 1){ 
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  else if(length(factors) == 2){ 
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'mean')", sep="")))
  }else{
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  
  std_data$data_y = std_data$data_y / sqrt(numOfSub)
  
  ribbondata$SE_min <- ribbondata$data_y - std_data$data_y
  ribbondata$SE_max <- ribbondata$data_y + std_data$data_y
  # , color = ", factors[1],, color = ", factors[1],aes(shape = ", factors[2],"), 
  if(length(factors) == 1){ 
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y))", sep="")))
    eval(parse(text=paste("p = p + geom_point(size = 3,color='black')", sep="")))
  } else if(length(factors) == 2){
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, group = ",factors[2],"))", sep="")))
    eval(parse(text=paste("p = p + geom_point(size = 3)", sep="")))
  } else{
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, color = ", factors[1],", group = ",factors[2],"))", sep="")))
    eval(parse(text=paste("p = p + geom_point(aes(shape = ", factors[2],"), size = 3)", sep="")))
  }
  
  # eval(parse(text=paste("p = p + geom_point(aes(shape = ", factors[1],"), size = 3)", sep="")))
  if(!is.null(config$grCol)){
    p = p + scale_color_manual(values = config$grCol)
  }
  # geom_line() +
  # scale_color_manual(values = config$grCol)+
  # scale_color_viridis(discrete = TRUE)+
  p = p +  
    # geom_line()+
    geom_errorbar(aes(ymin = SE_min, ymax = SE_max),size = 0.1, width = 0.1,color="black")+ 
    xlab(config$label_x) + ylab(config$label_y) +
    theme(
      axis.ticks.x = element_blank(),
      # axis.text.x = element_text(angle = 30, hjust = 1),
      axis.line.x = element_blank()
    )
  
  return(p)
}

dispBarGraph <- function(ribbondata, config, factors,numOfSub = 0){
  
  if(numOfSub == 0) {numOfSub = length(unique(ribbondata$sub))}
  
  if(length(factors) == 1){
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  else if(length(factors) == 2){
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'mean')", sep="")))
  }else{
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  
  std_data$data_y = std_data$data_y / sqrt(numOfSub)
  
  ribbondata$SE_min <- ribbondata$data_y - std_data$data_y
  ribbondata$SE_max <- ribbondata$data_y + std_data$data_y
  
  if(length(factors) == 1){ 
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y,color =",factors[1] ,",fill =",factors[1] ,"))", sep="")))
  } else if(length(factors) == 2){
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, color=interaction(",factors[1],",",factors[2],"),fill = interaction(",factors[1],",",factors[2],")))", sep="")))
  } else{
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, color = interaction(", factors[1],",",factors[2],",",factors[3],"),",
                          "fill = interaction(", factors[1],",",factors[2],",",factors[3],")","))", sep="")))
  }
  
  p <- p + 
    geom_bar(stat = "identity", position = "dodge")+
    geom_errorbar(aes(ymin = SE_min, ymax = SE_max),
                  width = 0.3, size=0.2, position = position_dodge(.9)) +
    geom_hline(yintercept=0, colour="black", linetype="solid", size = 0.5) +
    xlab(config$label_x) + ylab(config$label_y) + 
    theme(
      axis.ticks.x = element_blank(),
      # axis.text.x = element_text(angle = 30, hjust = 1),
      axis.line.x = element_blank()
    )
  
  if(!is.null(config$grCol)){
    p=p+scale_fill_manual(values = config$grCol)+
      scale_color_manual(values = config$gr_outline)
  }
  
  return(p)
}

```

# making dataset e1
```{r, message=FALSE, warning=FALSE}
sTime = -0.2
eTime = 4

gColor = rep(c("Black","Blue","Cyan","Green","Yellow","Red","Magenta"),2)
gPattern = c("Glare","Halo")

# #### making dataset for e1 #################################

dat <- readMat("./data/data1.mat")
numOfTrial = dim(dat$y)[1]
numOfSub = length(unique(dat$sub))
lengthOfTime = dim(dat$y)[2]

x = seq(sTime,eTime,length=lengthOfTime)
sh = rep(c(1,2),times=c(7,7))

ind_data <- data.frame(
  sub =  rep( dat$sub, times = rep( lengthOfTime, numOfTrial)),
  data_y = t(matrix(t(dat$y),nrow=1)),
  data_x = rep( x, numOfTrial),
  Color = rep( dat$condition, times = rep(lengthOfTime, numOfTrial)),
  Pattern = rep( sh[dat$condition], times = rep(lengthOfTime, numOfTrial))
 )
ind_data$Color = gColor[ind_data$Color]
ind_data$Color <- factor(ind_data$Color, levels = c("Black","Blue","Cyan","Green","Yellow","Red","Magenta"))

ind_data$Pattern = gPattern[ind_data$Pattern]

data_e1 = aggregate( data_y ~ sub*Color*Pattern*data_x, data = ind_data, FUN = "mean")

dat_mean = unlist(tapply(data_e1$data_y,list(data_e1$sub,data_e1$Color,data_e1$Pattern),min))
dat_mean = matrix(dat_mean,ncol = 1)

save(data_e1,file = "dataset_e1.rda")
```

# making dataset e2
```{r, message=FALSE, warning=FALSE}
# #### making dataset for e2 #################################
dat = readMat("./data/data_e2.mat")

numOfTrial = dim(dat$datRes)[1]
numOfSub = length(unique(dat$sub))
sType = rep(1:2,times=c(7,7))
ind_data = data.frame(
  sub =  dat$sub,
  data_y = dat$datRes,
  Color = dat$condition,
  Pattern = sType[dat$condition]
 )

ind_data$Color = gColor[ind_data$Color]
ind_data$Color = factor(ind_data$Color, levels = c("Black","Blue","Cyan","Green","Yellow","Red","Magenta"))

ind_data$Pattern = gPattern[ind_data$Pattern]
ind_data$Pattern = factor(ind_data$Pattern, levels = gPattern)

ind_data = ind_data[order(ind_data$sub, ind_data$Color, ind_data$Pattern),]
dat_mean = matrix(tapply(ind_data$data_y,list(ind_data$Pattern,ind_data$Color,ind_data$sub),mean),ncol = 1)
dat_sd = matrix(tapply(ind_data$data_y,list(ind_data$Pattern,ind_data$Color,ind_data$sub),sd),ncol = 1)

dat_sd = dat_sd*3
ind_data$dat_mean = rep(dat_mean,times = rep(8,14*numOfSub))
ind_data$minsd = ind_data$dat_mean - rep(dat_sd,times = rep(8,14*numOfSub))
ind_data$maxsd = ind_data$dat_mean + rep(dat_sd,times = rep(8,14*numOfSub))

ind_data = ind_data[ind_data$data_y < ind_data$maxsd,]
ind_data = ind_data[ind_data$data_y > ind_data$minsd,]

data_e2 = aggregate( data_y ~ sub*Color*Pattern, data = ind_data, FUN = "mean")

cri = data_e2[ data_e2$Color == "Black" & data_e2$Pattern == "Halo",]
cri = rep(cri$data_y,14)
data_e2$data_afy = mapply(function(x,y){return (x/y)},data_e2$data_y,cri)

data_e2$data_afy = data_e2$data_afy*100 -100

save(data_e2,file = "dataset_e2.rda")
```


# making dataset e3
```{r, message=FALSE, warning=FALSE}
#### making dataset for e3 #################################
dat <- readMat("./data/data_e3.mat")

numOfTrial = dim(dat$y)[1]
numOfSub = length(unique(dat$sub))
lengthOfTime = dim(dat$y)[2]

x = seq(sTime,eTime,length=lengthOfTime)

ind_data <- data.frame(
  sub =  rep( dat$sub, times = rep( lengthOfTime, numOfTrial)),
  data_y = t(matrix(t(dat$y),nrow=1)),
  data_x = rep( x, numOfTrial),
  Color = rep( gColor[dat$condition], times = rep(lengthOfTime, numOfTrial))
    )
ind_data$Pattern = "Homogeneous"

data_e3 = aggregate( data_y ~ sub*Color*Pattern*data_x, data = ind_data, FUN = "mean")
g <- c("Black","Blue","Cyan","Green","Yellow","Red","Magenta")
data_e3$Color <- factor(data_e3$Color, levels = g)

save(data_e3,file = "dataset_e3.rda")
```

# Figure 3ab
```{r, message=FALSE, warning=FALSE}

sTime = -0.2
eTime = 4
countFigNum = 1

#### file loading 
load("dataset_e1.rda")

numOfSub = length(unique(data_e1$sub))
subName = NULL
for( i in seq(max(data_e1$sub))){ subName = rbind(subName,paste("s", i, sep = ""))}
data_e1$sub = subName[data_e1$sub]

### show graph
data_e1_ave = aggregate( data_y ~ Color*Pattern*data_x, data = data_e1, FUN = "mean")

config <- list(lim_x = c(sTime, eTime),
               lim_y = c(min(data_e1_ave$data_y), max(data_e1_ave$data_y)),
               alpha = 0.1,
               stride = 0.1,
               label_x = "Time [sec]",
               label_y = "Pupil Changes [mm]",
               title = "pupil",
               grCol = rep(c("Black","Blue","Cyan","Green","Yellow","Red","Magenta"),2)
)

p <- disp(data_e1_ave,config,0,c("Color","Color"))
p <- p + facet_grid(. ~ Pattern)

p = setFigureStyle(p)

p <- p + theme(
  legend.position = 'none'
)
eval(parse(text=paste("p", countFigNum ,"=p", sep="")))
countFigNum = countFigNum+1

## mean during time from 0sec to 4sec
data_e1_anova = aggregate( data_y ~ sub*Color*Pattern, data = data_e1, FUN = "mean")

#### ANOVA
anovakun(data_e1_anova,"sAB",gg=T,long=T, peta=T)
# output2wayANOVA(forDrawingSigANOVA)
# sigPair = makeSigPair(forDrawingPost)

## mean during time from 0sec to 4sec
data_e1_plot = aggregate( data_y ~ Color*Pattern, data = data_e1_anova, FUN = "mean")
std_data = aggregate(data_y ~ Color*Pattern, data=data_e1_anova, FUN = "sd") 
std_data$data_y <- std_data$data_y / sqrt(numOfSub)

std_data$SE_min <- data_e1_plot$data_y - std_data$data_y
std_data$SE_max <- data_e1_plot$data_y + std_data$data_y

### bar plot
config <- list(lim_x = c(0.5,7.5),
               lim_y = c(min(std_data$SE_min), max(std_data$SE_max)),
               stride =c(-0.3,-0.2,-0.1,-0.0,0.1,0.2),
               label_x = "Condition",
               label_y = "Averaged Pupil Changes [mm]",
               title="average",
               gr = c("Black","Blue","Cyan","Green","Yellow","Red","Magenta",
                      "#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF"),
               gr_outline = rep(c("Black","Blue","Cyan","Green","Yellow","Red","Magenta"),times=rep(2,7))
)

p <- ggplot(data_e1_plot, aes(x = Color, y = data_y, fill = interaction(Color,Pattern)))+
  geom_bar(stat = "identity", position = "dodge", colour = config$gr_outline)+
  # scale_fill_manual(values = c("blue","white")) +
  scale_fill_manual(values = config$gr) +
  
  geom_errorbar(data = std_data, aes(ymin = SE_min, ymax = SE_max),
                width = 0.3, size=0.2, position = position_dodge(.9) ) +
  
  geom_hline(yintercept=0, colour="black", linetype="solid", size = 0.5) +
  # ylim(config$lim_y) + 
  xlab(config$label_x) + ylab(config$label_y)

# p <- drawSignificance(p,sigPair,0.12,0.015)

p = setBarFigureStyle(p)
p <- p + theme(
  legend.position = 'none',
  axis.ticks.x = element_blank(),
  axis.text.x = element_text(angle = 30, hjust = 1),
  axis.line.x = element_blank()
)
eval(parse(text=paste("p", countFigNum ,"=p", sep="")))
countFigNum = countFigNum+1

# figure output -----------------------------------------------------------

p = ggarrange(p1, p2,
              labels = c("(a)", "(b)"),
              ncol = 2, nrow = 1)
plot(p)
```

# Figure 4a
```{r, message=FALSE, warning=FALSE}

countFigNum = 1
SIZE_FONT=20

#### file loading 
load("dataset_e2.rda")

# exclude the participants rejected in pupillometry(exp1)
data_e2 <- subset(data_e2, sub != 7 & sub != 13 & sub != 9)

numOfSub = length(unique(data_e2$sub))
numOfcondition = 14
anova_data_e2 <- aggregate( data_afy ~ sub*Color*Pattern, data = data_e2, FUN = "mean")

anovakun(anova_data_e2,"sAB",gg=T,long=T, peta=T)
# output2wayANOVA(forDrawingSigANOVA)
# sigPair = makeSigPair(forDrawingPost)

####
config = list(lim_x=c(0.5,8),
              lim_y = c(-5,25),
              stride = 10,
              label_x = "",
              label_y = "Adjusted luminance score [%]",
              title="average",
              gr = c("Black","Blue","Cyan","Green","Yellow","Red","Magenta",
                     "#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF","#FFFFFF"),
              gr_outline = rep(c("Black","Blue","Cyan","Green","Yellow","Red","Magenta"),times=rep(2,7))
)
config$stride = round(seq(config$lim_y[1],config$lim_y[2],config$stride),1)

jitterVal <- c(rep(-0.225,numOfSub*(numOfcondition/2)),rep(0.225,numOfSub*(numOfcondition/2)))

data_e2_ave <- aggregate( data_afy ~ Color*Pattern, data = data_e2, FUN = "mean")
std_data = aggregate(data_afy ~ Color*Pattern, data=data_e2, FUN = "sd") 
std_data$data_afy <- std_data$data_afy / sqrt(numOfSub)

SE_min <- data_e2_ave$data_afy - std_data$data_afy
SE_max <- data_e2_ave$data_afy + std_data$data_afy

p <- ggplot(data_e2_ave, aes(x = Color, y = data_afy, fill = interaction(Color,Pattern)))+
  geom_bar(stat = "identity", position = "dodge", colour = config$gr_outline)+
  scale_fill_manual(values = config$gr) +
   geom_hline(yintercept=0, colour="black", linetype="solid", size = 0.5) +
  geom_errorbar(aes(ymin = SE_min, ymax = SE_max),
                width = 0.4,
                size=0.2,
                position=position_dodge(.9)) +
  coord_cartesian(xlim = config$lim_x, ylim = config$lim_y)+
  xlab(config$label_x) + ylab(config$label_y)+ 
  scale_y_continuous(breaks = config$stride,expand = c(0, 0))


p = setBarFigureStyle(p)
# p <- drawSignificance(p,sigPair,37,1)

p <- p + theme(
  legend.position = 'none',
  axis.ticks.x = element_blank(),
  axis.text.x = element_text(angle = 30, hjust = 1),
  axis.line.x = element_blank()
)

# # # figure output -----------------------------------------------------------
plot(p)
```

# Figure 4b
```{r, message=FALSE, warning=FALSE}

load("dataset_e2.rda")
# exclude the participants rejected in pupillometry(exp1)
data_e2 <- subset(data_e2, sub != 7 & sub != 8 & sub != 13)
data_e2 <- data_e2[data_e2$Pattern == "Glare",]

load("dataset_e1.rda")
data_e1 = aggregate( data_y ~ sub*Color*Pattern, data = data_e1, FUN = "mean")
# exclude the participants who had a noisy pupil data or didn"t participante in exp2"
data_e1 <- subset(data_e1, sub != 7 & sub != 13 & sub < 18)

data_e1 <- data_e1[data_e1$Pattern == "Glare",]
data_e2$PLR <- data_e1$data_y

subName = NULL
for( i in seq( length(unique(data_e2$sub))) ){ 
  subName = rbind(subName,paste("s", i, sep = ""))
}
data_e2$sub = rep(subName, numOfcondition/2)

config = list(lim_x = c(-20, 40),
              lim_y = c(-1, 0.7),
              stride = c(-0.4,-0.0,0.4),
              alpha_val = 0.7,
              label_x = "Adjusted luminance score [%]",
              label_y = "Pupil Changes [mm]",
              grCol= c("Black","Blue","Cyan","Green","Magenta","Red","Yellow"))

data_e2_ave = aggregate(data_e2, by=list(Color=data_e2$Color,Pattern=data_e2$Pattern), FUN = "mean")

p_val = NULL
indCoff_y = NULL
for( i in 1:numOfcondition ){
  tmpData = data_e2[data_e2$sub == subName[i],]
  lm = lm(PLR ~ data_afy, data = tmpData)
  newavg <- data.frame(data_afy = config$lim_x[1]:config$lim_x[2])
  newavg$reaction <- predict(lm, re.form = NA, newavg)
  indCoff_y = cbind(indCoff_y,newavg$reaction)
  p_val =  cbind(round(summary(lm)$coefficients[2,"Pr(>|t|)"], digits = 4))
}

indCoff <- data.frame(
  y = matrix(indCoff_y,ncol = 1),
  x = newavg$data_afy,
  sub = rep(subName,times=rep( dim(newavg)[1], numOfcondition))
)

lm = lmer(PLR ~ data_afy + (1+data_afy|sub), data = data_e2)
print(paste("y = ", round(summary(lm)$coefficients[2,"Estimate"], digits = 4),
            "x + ", round(summary(lm)$coefficients[1,"Estimate"], digits = 4),
            ", t = ", round(summary(lm)$coefficients[2,"t value"], digits = 4),
            ", p = ", round(summary(lm)$coefficients[2,"Pr(>|t|)"], digits = 4),
            ", R = ", round(cor(data_e2$data_afy,data_e2$PLR), digits = 4), sep=""))


# Data frame to evaluate average effects predictions on
newavg <- data.frame(data_afy = (config$lim_x[1]-20):(config$lim_x[2]+20))
newavg$reaction <- predict(lm, re.form = NA, newavg)

p <- ggplot() +
  geom_line(data = newavg,aes(x = data_afy, y=reaction), col = "black", size = 1) +
  geom_point(data = data_e2, alpha = config$alpha_val,
             aes(x = data_afy, y = PLR, colour = Color, fill = Color), size = 2) +
  scale_color_manual(values = config$gr) +
  xlim(config$lim_x) +
  xlab(config$label_x) + 
  ylab(config$label_y)

p <- setFigureStyle(p)
p <- p + theme(
  # legend.position = 'none',
  axis.line.x = element_blank(),
  axis.line.y = element_blank()
)

## figure output -----------------------------------------------------------
print(p)

```