# Article information

Experimental data for "Pupillary constriction as an indicator of illusory luminosity perception in the glare illusion"

Yuta Suzuki, Takuya Fujii, Tetsuto Minami, Shigeki Nakauchi

*Corresponding author: Yuta Suzuki
NTT Communication Science Laboratories, NTT Corporation, Atsugi 243-0198, Japan
Tel: +81-046-240-3525 , E-mail: yuuta.suzuki.fc@hco.ntt.co.jp

# Package instalation
```{r, message=FALSE, warning=FALSE}
library(rjson)
library(ggplot2)
library(ggpubr)
library(Cairo)

if(exists(".anovakun.env")){
  sys.source("./data/anovakun_485.R", envir = .anovakun.env)
}else{
  .anovakun.env <- new.env()
  sys.source("./data/anovakun_485.R", envir = .anovakun.env)
  attach(.anovakun.env)
}
subName = NULL
for( i in seq(30)){ 
  if(i<10){subName = rbind(subName,paste("s0", i, sep = ""))} 
  else{subName = rbind(subName,paste("s", i, sep = ""))}
}

```

# Function definition
```{r, message=FALSE, warning=FALSE}
combineGraphs <- function(graphNum,p,layout){
  
  titleStr = c("'(a)'", "'(b)'", "'(c)'", "'(d)'", "'(e)'", "'(f)'", "'(g)'")
  st = paste(p,graphNum, sep = "", collapse=",")
  labelSt = titleStr[seq(1,length(graphNum))]
  labelSt = paste(labelSt, collapse=",")
  
  ncolNum = round(length(graphNum) / 2 )
  
  if (is.numeric(layout)){
    eval(parse(text=paste("p = grid.arrange(", 
                          st ,",layout_matrix = layout)",
                          sep="")))
  }else{
    eval(parse(text=paste("p = ggarrange(",
                          st ,",labels = c(",
                          labelSt,
                          "),ncol = 2, nrow =", ncolNum, ")",
                          sep="")))
  }
  return(p)
}

makePupilDataset_mat2long <- function(dat,nameOfVar, timeLen,fNum,orderName,factors){
  
  numOfTrial = dim(dat$y)[1]
  numOfSub = length(unique(dat$sub))
  lengthOfTime = dim(dat$y)[2]
  
  sTime = timeLen[1]
  eTime = timeLen[2]
  
  x = seq(sTime,eTime,length=lengthOfTime)
  
  ind_data <- data.frame(
    sub =  rep( dat$sub, times = rep( lengthOfTime, numOfTrial)),
    data_y = t(matrix(t(dat$y),nrow=1)),
    data_x = x
  )
  
  if (length(nameOfVar)  == 1){
    eval(parse(text=paste("ind_data$",factors[[1]],"=",
                          "rep( fNum[[1]][dat$",nameOfVar[[1]],"], times = rep(lengthOfTime, numOfTrial))",
                          sep="")))
    
    eval(parse(text=paste("ind_data$",factors[[1]],"<-",
                          "factor(ind_data$", factors[[1]],",levels = orderName[[1]])", sep="")))
    
  }else{
    eval(parse(text=paste("ind_data$",factors[[1]],"=",
                          "rep( fNum[[1]][dat$", nameOfVar[[1]],"], times = rep(lengthOfTime, numOfTrial))",
                          sep="")))
    eval(parse(text=paste("ind_data$",factors[[2]],"=",
                          "rep( fNum[[2]][dat$" , nameOfVar[[2]], "], times = rep(lengthOfTime, numOfTrial))",
                          sep="")))
    
    eval(parse(text=paste("ind_data$",factors[[1]],"<-",
                          "factor(ind_data$", factors[[1]],",levels = orderName[[1]])", sep="")))
    eval(parse(text=paste("ind_data$",factors[[2]],"<-",
                          "factor(ind_data$", factors[[2]],",levels = orderName[[2]])", sep="")))
  }
  
  return(ind_data)
}

setFigureStyle <- function(gData,size_font=20){
  gData <- gData +theme(
    axis.title.x = element_text(size=size_font),
    axis.title.y = element_text(size=size_font),
    axis.line = element_line(colour = "black"),
    axis.text.x = element_text(colour="black"),
    axis.text.y = element_text(colour="black"),
    panel.background = element_rect(fill = "transparent",color = 'black',size = 0.5),
    panel.grid.major = element_line(colour = "gray", size = 0.05),
    panel.grid.minor = element_line(colour = NA),
    axis.ticks = element_line(colour = "black",size = 0.5),
    text = element_text(size = size_font,family = "Times"),
    # text = element_text(size = size_font,family = "Source Han Sans JP ExtraLight"),
    # text = element_text(size = 16,family = "Helvetica"),
    legend.title = element_text(size=(size_font/3)),
    legend.text = element_text(size=(size_font/2)),
    legend.key=element_rect(colour="transparent", fill=NA),
    plot.background=element_rect(fill="transparent", colour=NA),
    legend.background=element_rect(fill="transparent", colour=NA),
    plot.title = element_text(size = size_font)
    # axis.line = element_line(colour = 'black', size = 2)
  )
  return(gData)
}

setBarFigureStyle <- function(gData,size_font=20){
  gData <- gData +theme(
    axis.title.x = element_text(size=size_font),
    axis.title.y = element_text(size=size_font),
    panel.border = element_blank(), 
    axis.line = element_line(),
    axis.text.x = element_text(colour="black"),
    axis.text.y = element_text(colour="black"),
    panel.background = element_rect(fill = "transparent",size = 0.5),
    # panel.grid.major = element_line(colour = NA),
    panel.grid.major.y = element_line(colour = "gray", size = 0.05),
    panel.grid.major.x = element_line(colour = NA),
    panel.grid.minor = element_line(colour = NA),
    axis.ticks = element_line(colour = "black",size = 0.5),
    text = element_text(size = size_font,family = "Times"),
    # text = element_text(size = size_font,family = "Source Han Sans JP ExtraLight"),
    legend.title = element_text(size=(size_font/2)),
    legend.text = element_text(size=(size_font/2)),
    legend.key=element_rect(colour="transparent", fill=NA),
    plot.background=element_rect(fill="transparent", colour=NA),
    legend.background=element_rect(fill="transparent", colour=NA),
    plot.title = element_text(size = size_font)
  )
  return(gData)
}

disp <- function(ribbondata,config,shadeFl,factors,numOfSub=0){
  
  if (shadeFl == 1) {
    if(numOfSub == 0) {numOfSub = length(unique(ribbondata$sub))}
    eval(parse(text=paste(
      "data_std = aggregate( data_y ~ data_x * ",factors[1],"*",factors[2],
      ", data = ribbondata, FUN = 'sd')",
      sep=""))) 
    eval(parse(text=paste(
      "ribbondata = aggregate( data_y ~ data_x * ",factors[1],"*",factors[2],
      ", data = ribbondata, FUN = 'mean')",
      sep="")))
    
    data_std$data_y <- data_std$data_y / sqrt(numOfSub)
    ribbondata$ymin <- ribbondata$data_y - data_std$data_y
    ribbondata$ymax <- ribbondata$data_y + data_std$data_y
    
    eval(parse(text=paste(
      "p <- ggplot(ribbondata,
      aes(x = data_x, y = data_y, colour = ", factors[1],", group = ",factors[1],"))+",
      # "annotation_raster(image, -Inf, Inf, -Inf, Inf) +",
      "geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = ",factors[2],", group = ",factors[1], "), color = 'gray', fill = 'gray', alpha = config$alpha, size = 0.05) +",
      "geom_line()",
      # "geom_line(aes(linetype=",factors[1],"))",
      sep="")))
    
    if(!is.null(config$grCol)){
      p <- p +
        # scale_color_manual(values = config$grCol, name = factors[1])+
        scale_fill_manual(values = config$grCol)+
        scale_color_manual(values = config$grCol)
    }
    
    p <- p +
      ggtitle(config$title) +
      xlab(config$label_x) + ylab(config$label_y) +
      coord_cartesian(xlim = config$lim_x,ylim = config$lim_y) +
      scale_x_continuous(expand = c(0, 0)) 
    
  }else{ 
    
    eval(parse(text=paste(
      "p <- ggplot(ribbondata,aes(x = data_x, y = data_y, colour = ", factors[1],", group = ",factors[2],"))+", 
      # "geom_line(aes(linetype = Type))",
      "geom_line()",
      sep="")))
    
    if(!is.null(config$grCol)){
      p <- p +
        scale_color_manual(values = config$grCol)
    }
    p <- p + 
      geom_vline(xintercept=0, colour='black', linetype='longdash', size = 0.1) +
      ggtitle(config$title) +
      xlab(config$label_x) + ylab(config$label_y) +
      coord_cartesian(xlim=config$lim_x, ylim=config$lim_y) +
      scale_x_continuous(expand = c(0, 0))
    # scale_y_continuous(expand = c(0, 0.1))
    # scale_y_continuous(breaks = seq(config$lim_y[1],config$lim_y[2],config$stride),expand = c(0, 0))
    
  }
  
  p = setBarFigureStyle(p)
  
  return(p)
}


dispLineGraph <- function(ribbondata, config, factors,numOfSub = 0){
  
  if(numOfSub == 0) {numOfSub = length(unique(ribbondata$sub))}
  
  if(length(factors) == 1){ 
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  else if(length(factors) == 2){ 
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'mean')", sep="")))
  }else{
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  
  std_data$data_y = std_data$data_y / sqrt(numOfSub)
  
  ribbondata$SE_min <- ribbondata$data_y - std_data$data_y
  ribbondata$SE_max <- ribbondata$data_y + std_data$data_y
  # , color = ", factors[1],, color = ", factors[1],aes(shape = ", factors[2],"), 
  if(length(factors) == 1){ 
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y))", sep="")))
    eval(parse(text=paste("p = p + geom_point(size = 3,color='black')", sep="")))
  } else if(length(factors) == 2){
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, group = ",factors[2],"))", sep="")))
    eval(parse(text=paste("p = p + geom_point(size = 3)", sep="")))
  } else{
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, color = ", factors[1],", group = ",factors[2],"))", sep="")))
    eval(parse(text=paste("p = p + geom_point(aes(shape = ", factors[2],"), size = 3)", sep="")))
  }
  
  # eval(parse(text=paste("p = p + geom_point(aes(shape = ", factors[1],"), size = 3)", sep="")))
  if(!is.null(config$grCol)){
    p = p + scale_color_manual(values = config$grCol)
  }
  # geom_line() +
  # scale_color_manual(values = config$grCol)+
  # scale_color_viridis(discrete = TRUE)+
  p = p +  
    # geom_line()+
    geom_errorbar(aes(ymin = SE_min, ymax = SE_max),size = 0.1, width = 0.1,color="black")+ 
    xlab(config$label_x) + ylab(config$label_y) +
    theme(
      axis.ticks.x = element_blank(),
      # axis.text.x = element_text(angle = 30, hjust = 1),
      axis.line.x = element_blank()
    )
  
  return(p)
}

dispBarGraph <- function(ribbondata, config, factors,numOfSub = 0){
  
  if(numOfSub == 0) {numOfSub = length(unique(ribbondata$sub))}
  
  if(length(factors) == 1){
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  else if(length(factors) == 2){
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2], ", data = ribbondata, FUN = 'mean')", sep="")))
  }else{
    eval(parse(text=paste("std_data = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'sd')", sep="")))
    eval(parse(text=paste("ribbondata = aggregate( data_y ~ ",factors[1],"*",factors[2],"*",factors[3], ", data = ribbondata, FUN = 'mean')", sep="")))
  }
  
  std_data$data_y = std_data$data_y / sqrt(numOfSub)
  
  ribbondata$SE_min <- ribbondata$data_y - std_data$data_y
  ribbondata$SE_max <- ribbondata$data_y + std_data$data_y
  
  if(length(factors) == 1){ 
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y,color =",factors[1] ,",fill =",factors[1] ,"))", sep="")))
  } else if(length(factors) == 2){
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, color=interaction(",factors[1],",",factors[2],"),fill = interaction(",factors[1],",",factors[2],")))", sep="")))
  } else{
    eval(parse(text=paste("p <- ggplot(ribbondata,aes(x = ", factors[1],", y = data_y, color = interaction(", factors[1],",",factors[2],",",factors[3],"),",
                          "fill = interaction(", factors[1],",",factors[2],",",factors[3],")","))", sep="")))
  }
  
  p <- p + 
    geom_bar(stat = "identity", position = "dodge")+
    geom_errorbar(aes(ymin = SE_min, ymax = SE_max),
                  width = 0.3, size=0.2, position = position_dodge(.9)) +
    geom_hline(yintercept=0, colour="black", linetype="solid", size = 0.5) +
    xlab(config$label_x) + ylab(config$label_y) + 
    theme(
      axis.ticks.x = element_blank(),
      # axis.text.x = element_text(angle = 30, hjust = 1),
      axis.line.x = element_blank()
    )
  
  if(!is.null(config$grCol)){
    p=p+scale_fill_manual(values = config$grCol)+
      scale_color_manual(values = config$gr_outline)
  }
  
  return(p)
}

```

# making dataset e1
```{r, message=FALSE, warning=FALSE}

timeLen = c(-0.2, 4)
# the condition types are described as below
f1 = "Pattern"
f2 = "Shape"
g1 <- c("Radial", "Radial", "Control", "Control")
g2 <- c("Kanizsa", "No-triangle", "Kanizsa", "No-triangle")

fNum = list(g1,g2)
orderName = list(c("Radial", "Control"),c("Kanizsa", "No-triangle"))
factors = list(f1,f2)

#### making dataset for e1 #################################
data=fromJSON(file="./data/data_e1.json")
dat <- list(matrix(unlist(data$y),nrow=length(data$y),byrow=T),
            matrix(unlist(data$gazeX),nrow=length(data$gazeX),byrow=T),
            matrix(unlist(data$gazeY),nrow=length(data$gazeY),byrow=T),
            t(unlist(data$sub)),t(unlist(data$condition)))
names(dat) <- c('y','gazeX','gazeY', 'sub', 'condition')

ind_data = makePupilDataset_mat2long(dat,c('condition','condition'),timeLen,fNum,orderName,factors)
gazeX = t(matrix(t(dat$gazeX),nrow=1))
ind_data = cbind(ind_data,gazeX)
gazeY = t(matrix(t(dat$gazeY),nrow=1))
ind_data = cbind(ind_data,gazeY)

data_e1 = aggregate( . ~ sub*data_x*Pattern*Shape, data = ind_data, FUN = "mean")
data_e1$gazeX = round(data_e1$gazeX, digits = 0)
data_e1$gazeY = round(data_e1$gazeY, digits = 0)

save(data_e1,file = "dataset_e1.rda")
```

# making dataset e2
```{r, message=FALSE, warning=FALSE}

# the condition types are described as below
f1 = "Pattern"
g1 <- c("Radial", "Control")

#### making dataset for e1 #################################
dat = fromJSON(file="./data/data_e2.json")
lut = unlist(fromJSON(file="./data/data_disp.json"))

numOfSub = length(unique(dat$sub))

ind_data <- data.frame(
  sub =  dat$sub,
  data_y = ((lut[round(dat$taskRes,digit=0)]/86)*100)-100,
  locs = dat$locs,
  Pattern = g1[dat$condition]
)
eval(parse(text=paste("ind_data$",f1, "<- factor(ind_data$",f1, ",levels = c('",paste(g1,collapse="','"),"'))",sep="")))

ind_data = ind_data[order(ind_data$Pattern,ind_data$sub),]

dat_mean = tapply(ind_data$data_y,list(ind_data$sub,ind_data$Pattern),mean)
dat_sd = tapply(ind_data$data_y,list(ind_data$sub,ind_data$Pattern),sd)
dat_sdAll = sd(ind_data$data_y)

dat_mean = matrix(dat_mean,ncol = 1)
dat_sd = matrix(dat_sd,ncol = 1)
dat_sd = rep(dat_sdAll,42)
dat_mean = rep(dat_mean,times = rep(16,numOfSub*2))
ind_data = cbind(ind_data,dat_mean)

ind_data$minsd = ind_data$dat_mean - rep(dat_sd,times = rep(16,numOfSub*2))
ind_data$maxsd = ind_data$dat_mean + rep(dat_sd,times = rep(16,numOfSub*2))

dat_sd = rep(dat_sd,times = rep(16,numOfSub*2))
ind_data = cbind(ind_data,dat_sd)

ind_data = ind_data[ind_data$data_y < ind_data$maxsd,]
ind_data = ind_data[ind_data$data_y > ind_data$minsd,]

data_e2 = aggregate( data_y ~ sub*Pattern, data = ind_data, FUN = "mean")

save(data_e2,file = "dataset_e2.rda")
```

# making dataset e3
```{r, message=FALSE, warning=FALSE}

sTime = -0.2
eTime = 4

#### the condition types are described as below
f1 = "Angle"
f2 = "Pattern"
g1 <- c("0.97", "0.84", "0.56", "0.46", "0","0.46", "0.56", "0.84", "0.97")
g2 <- rep(c("Glare","Uniform","Halo"),times=c(4,1,4))
go1 = c("0.97", "0.84", "0.56", "0.46", "0")
go2 = c("Glare","Uniform","Halo")

#### making dataset for e1 #################################
data=fromJSON(file="./data/data_e3.json")
dat <- list(matrix(unlist(data$y),nrow=length(data$y),byrow=T),
            t(unlist(data$sub)),t(unlist(data$condition)),t(unlist(data$taskRes)))
names(dat) <- c('y', 'sub', 'condition', 'taskRes')

numOfTrial = dim(dat$y)[1]
numOfSub = length(unique(dat$sub))
lengthOfTime = dim(dat$y)[2]
timeLen = c(sTime,eTime)

x = seq(sTime,eTime,length=lengthOfTime)

ind_data = makePupilDataset_mat2long(dat,c('condition','condition'),timeLen,list(g1,g2),list(go1,go2),c(f1,f2))

data_e1 = aggregate( data_y ~ sub*data_x*Angle*Pattern, data = ind_data, FUN = "mean")
data_e1_all = ind_data

xdur = c(58,54,42,38,0,-38,-42,-54,-58)
xorder = rep(c(1,0,2),times=c(4,1,4))

ind_data <- data.frame(
  sub =  t(dat$sub),
  data_y = t(dat$taskRes),
  n = matrix(1,dim(dat$taskRes)[1]*dim(dat$taskRes)[2],1),
  cell = xdur[dat$condition]
)
eval(parse(text=paste("ind_data$",f1,"=",
                      "g1[dat$condition]",
                      sep="")))
ind_data$Angle <- factor(ind_data$Angle, levels = go1)

eval(parse(text=paste("ind_data$",f2,"=",
                      "g2[dat$condition]",
                      sep="")))

ind_data$Pattern <- factor(ind_data$Pattern, levels = c("Glare","Uniform","Halo"))
data_task = ind_data

save(data_e1,data_task,data_e1_all,file = "dataset_e3.rda")
```

# Figure 3ab
```{r, message=FALSE, warning=FALSE}

countFigNum = 1
SIZE_FONT=20

#### file loading 
load("dataset_e1.rda")
numOfSub = length(unique(data_e1$sub))
sTime = -0.2
eTime = max(data_e1$data_x)

# time course of pupil ---------------------------------------------------
data_e1_ave = aggregate( data_y ~ data_x*Shape*Pattern, data = data_e1, FUN = "mean")

config = list(lim_x = c(sTime, eTime),
              lim_y = c(-0.05, 0.2),
              alpha = 0.4,
              stride = 0.1,
              label_x = "Time [sec]",
              label_y = "Averaged Pupil Changes [mm]",
              title = "",
              grCol = c("#000000","#808080")
)

p <- disp(data_e1,config,1,c("Pattern","Shape"))
p <- p + 
  facet_grid(. ~ Shape)

p = setFigureStyle(p,SIZE_FONT)

p <- p + theme(
  legend.position = c(0.9,0.2)
)

eval(parse(text=paste("p", countFigNum ,"=p", sep="")))
countFigNum = countFigNum+1


# mean during time from 0sec to 4sec --------------------------------------
data_e1 = data_e1[data_e1$data_x >= 0,]

# # #### ANOVA
print("-----------------------------------------")
print("          averaged in pupil size         ")
print("-----------------------------------------")
data_e1_anova = aggregate( data_y ~ sub*Pattern*Shape, data = data_e1, FUN = "mean")
anovakun(data_e1_anova,"sAB",gg=T,long=T, peta=T)

# ### bar plot
data_e1_plot = aggregate( data_y ~ Pattern*Shape, data = data_e1, FUN = "mean")
std_data = aggregate(data_y ~ Pattern*Shape, data = data_e1, FUN = "sd")
std_data$data_y <- std_data$data_y / sqrt(numOfSub)

data_e1_plot$SE_min <- data_e1_plot$data_y - std_data$data_y
data_e1_plot$SE_max <- data_e1_plot$data_y + std_data$data_y

data_e1_anova$cell   = rep(1:2, times = c(numOfSub,numOfSub))
data_e1_plot$cell  = rep(1:2,2)

p <- ggplot(data_e1_plot, aes(x = cell, y = data_y, group = Shape))+
  geom_bar(aes(fill = Pattern),color="black", stat = "identity", size=0.3) +
  scale_fill_manual(values = rep(c("black","white"),2)) +
  geom_errorbar(aes(ymin = SE_min, ymax = SE_max),
                width = 0.1, size=0.2, position = position_dodge(.9)) +
  geom_hline(yintercept=0, colour="black", linetype="solid", size = 0.3) +
  xlab("") + ylab(config$label_y)+
  scale_x_continuous(breaks = 1:2, 
                     labels = c(expression(paste("Radial")),
                                expression(paste("Control"))))

p = setBarFigureStyle(p,SIZE_FONT)
p <- p + facet_grid(. ~ Shape)

p <- p + theme(
  axis.title.x = element_blank(),
  legend.position = 'none',
  axis.ticks.x = element_blank(),
  axis.line.x = element_blank()
)

eval(parse(text=paste("p", countFigNum ,"=p", sep="")))
countFigNum = countFigNum+1

g = c("Kanizsa:radial","Kanizsa:control","No-triangle:radial","No-triangle:control")

numOfSub = length(unique(data_e1_anova$sub))

f = data.frame(
  sub = as.character(unique(data_e1_anova$sub)),
  y = matrix(data_e1_anova$data_y,nrow = numOfSub)
)

colnames(f) <- c("subject",g)
write.csv(f, "data/data_bayesian.csv",row.names=FALSE)

# # # figure output -----------------------------------------------------------
p = combineGraphs(seq(1,countFigNum-1),'p',NULL)
plot(p)
```

# Figure 3d
```{r, message=FALSE, warning=FALSE}

countFigNum = 1
SIZE_FONT=20

#### file loading 
load("dataset_e2.rda")
numOfSub = length(unique(data_e2$sub))

t.test(data_e2[data_e2$Pattern == 'Radial',]$data_y, mu=0)
t.test(data_e2[data_e2$Pattern == 'Control',]$data_y, mu=0)

# ANOVA -------------------------------------------------------------------
anovakun(data_e2,"sA",gg=T,long=T, peta=T)

# ### bar plot
config <- list(lim_x = c(0.5,7.5),
               lim_y = c(0,6),
               label_x = "",
               label_y = "Adjusted luminance [%]",
               title="average",
               grCol = c("#000000","#FFFFFF","#FFFFFF"),
               gr_outline = rep(c("#000000"),8)
)

p <- dispBarGraph(data_e2,config,c("Pattern"))+
  scale_y_continuous(breaks = seq(0,5),expand = c(0, 0.5))

p = setBarFigureStyle(p,SIZE_FONT)

p <- p + theme(
  axis.title.x = element_blank(),
  legend.position = 'none',
  axis.ticks.x = element_blank(),
  axis.line.x = element_blank()
)

g = c("Kanizsa:radial","Kanizsa:control")

numOfSub = length(unique(data_e2$sub))

f = data.frame(
  sub = as.character(unique(data_e2$sub)),
  y = matrix(data_e2$data_y,nrow = numOfSub)
)

colnames(f) <- c("subject",g)
write.csv(f, "data/data_e2_bayesian.csv",row.names=FALSE)

# # # figure output -----------------------------------------------------------
plot(p)
```

# Figure 4
```{r, message=FALSE, warning=FALSE}

CairoFonts(regular = "Times","Times")

sTime = -0.2
eTime = 4
countFigNum = 1
fontSize = 16

#### file loading 
load("dataset_e3.rda")
numOfSub = length(unique(data_e1$sub))
data_e1$sub = subName[data_e1$sub]

### show graph
data_e1_ave = aggregate( data_y ~ sub*Angle*Pattern*data_x, data = data_e1, FUN = "mean")
data_e1_ave = data_e1_ave[data_e1_ave$Pattern!='Uniform',]

data_e1_0deg = data_e1[data_e1$Pattern == 'Uniform',]
data_e1_0deg = aggregate( data_y ~ Angle*Pattern*data_x, data = data_e1_0deg, FUN = "mean")
data_e1_0deg = rbind(data_e1_0deg,data_e1_0deg,data_e1_0deg,data_e1_0deg,
                     data_e1_0deg,data_e1_0deg,data_e1_0deg,data_e1_0deg)

config = list(lim_x = c(sTime, eTime),
              lim_y = c(-0.5, 0.1),
              alpha = 0.4,
              stride = 0.1,
              label_x = "Time [sec]",
              label_y = "Pupil Changes [mm]",
              title = "(a)",
              grCol = rep(c("black", "gray16", "gray32", "gray48"),2),
              linetype = FALSE
)

p <- disp(data_e1_ave,config,1,c("Pattern","Angle")) +
  geom_line(aes(x = data_e1_0deg$data_x, y = data_e1_0deg$data_y),color='gray')

p <- p + facet_grid(Angle ~ .)

p = setFigureStyle(p)

p <- p + theme(
  legend.position = 'none'
)

eval(parse(text=paste("p", countFigNum ,"=p", sep="")))
countFigNum = countFigNum+1

# # ############# ANOVA ########################
print("-----------------------------------------")
print("           averaged pupil size           ")
print("-----------------------------------------")
data_e1_ave = data_e1_ave[data_e1_ave$data_x >= 0,]
data_e1_anova = aggregate( data_y ~ sub*Angle*Pattern, data = data_e1_ave, FUN = "mean")

anovakun(data_e1_anova,"sAB",gg=T,long=T, peta=T)

# bar plot ----------------------------------------------------------------
config <- list(lim_x = c(0.5,7.5),
               lim_y = c(-0.2,0),
               stride =c(-0.2,-0.1,-0.0,0.1,0.2),
               label_x = "",
               label_y = "Averaged Pupil Changes [mm]",
               title="average",
               grCol = rep(c("black", "gray16", "gray32", "gray48"),2)
)

data_e1_box = aggregate( data_y ~ sub*Angle*Pattern, data = data_e1, FUN = "mean")

p <- ggplot(data_e1_box,aes(x =Pattern,color =Angle,  y = data_y))+
  geom_boxplot(aes(linetype=Pattern))+
  scale_fill_manual(values = config$grCol)+
  scale_color_manual(values = config$grCol)+
  ylab(config$label_y)+
  facet_grid(. ~ Angle)

p = setBarFigureStyle(p,fontSize)

p <- p + theme(
  legend.position = 'none'
)

eval(parse(text=paste("p", countFigNum ,"=p", sep="")))
countFigNum = countFigNum+1

g <- c("Glare:0.97", "Glare:0.84", "Glare:0.56", "Glare:0.46", "0",
       "Halo:0.97", "Halo:0.84", "Halo:0.56", "Halo:0.46")

numOfSub = length(unique(data_e1_box$sub))

f = data.frame(
  sub = as.character(unique(data_e1_box$sub)),
  y = matrix(data_e1_box$data_y,nrow = numOfSub)
)

colnames(f) <- c("subject",g)
write.csv(f, "data/e3_bayesian.csv",row.names=FALSE)

load("dataset_e3.rda")
# data_task = aggregate( data_y ~ sub*Angle*Pattern, data = data_task, FUN = "mean")

# data_e1_box$task = data_task$data_y
# sd = aggregate( data_y ~ Angle*Pattern, data = data_e1_box, FUN = "sd") 
# sd$data_y = sd$data_y / sqrt(numOfSub)

sd_task = aggregate( data_y ~ Angle*Pattern, data = data_task, FUN = "sd")
sd_task$data_y = sd_task$data_y / sqrt(numOfSub)

data_task_ave = aggregate( data_y ~ Angle*Pattern, data = data_task, FUN = "mean")
# data_e1_box_ave$task = aggregate( task ~ Angle*Pattern, data = data_e1_box, FUN = "mean")$task

# data_e1_box_ave$SE_min_pupil = data_e1_box_ave$data_y - sd$data_y
# data_e1_box_ave$SE_max_pupil = data_e1_box_ave$data_y + sd$data_y 
data_task_ave$SE_min_task  = data_task_ave$data_y - sd_task$data_y
data_task_ave$SE_max_task  = data_task_ave$data_y + sd_task$data_y

g1 =  c(0.97,0.84,0.56,0.46,0,-0.46,-0.56,-0.84,-0.97)
g0 = c(58,54,42,38,0,-38,-42,-54,-58)

for(i in 1:length(g0)){
  data_task[data_task$cell == g0[i],]$cell = g1[i]
}

fit <- quickpsy(data_task, cell, data_y, n)
data_task_ave$Angle = g1

p <- ggplot(data_task_ave,aes(x = Angle, y = data_y )) +
  geom_errorbar(aes(ymin = SE_min_task, ymax = SE_max_task),width = 0.001, size=0.2) +
  # geom_errorbarh(aes(xmin= SE_min_pupil, xmax = SE_max_pupil),height = 0.01, size=0.2) +
  geom_point(aes(shape = Pattern,color = Angle,fill=Angle), size = 2)+
  xlab('Luminance contrast')+
  geom_line(data = fit$curves, aes(x = x, y = y))+
  # scale_fill_grey(start=0.8, end=0.2)
  # scale_fill_gradient(low = "black", high = "black") +
  scale_color_gradient(low = "gray10", high = "white") 

p = setBarFigureStyle(p,fontSize)
width_fig=4
height_fig=3

# ggsave(file = "test.eps",
#        plot = p, dpi = 100,
#        width = width_fig, height = height_fig,family="Times")


## figure output -----------------------------------------------------------
p = combineGraphs(seq(1,countFigNum-1),'p',NULL)
plot(p)
```